---
title: "Probability Theory"
---

::: callout-note
You can delete everything in here and start fresh.
:::

This is a `.qmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

To learn more about Quarto websites visit <https://quarto.org/docs/websites>.

# Assingment 1

```{r}
T_scope_on_time<-0.2
T_scope_not_time<-0.8
T_on_time<-0.6
T_not_time<-0.4
P_scope<-0.3
P_no_scope<-0.7

P_T_S<-P_scope*T_scope_on_time
P_T_nS<-P_no_scope*T_on_time
P_nT_S<-P_scope*T_scope_not_time
P_nT_nS<-P_no_scope*T_not_time

P_T_S
P_T_nS
P_nT_S
P_nT_nS

sum_P<-P_T_S+P_T_nS+P_nT_S+P_nT_nS

sum_P
```
# Assingment 2
What is the percentage of customers using all three devices?

0.5%

What is the percentage of customers using at least two devices?

19.4% 

What is the percentage of customers using only one device?

80.1%

# Assingment 3
```{r}
P_A<-0.04
P_nA<-1-P_A
P_BA<-0.97
P_BnA<-0.01

P_B<-P_BA*P_A+P_BnA*P_nA
P_AB<-(P_BA*P_A)/P_B
P_nAB<-(P_BnA*P_nA)/P_B

print(P_AB)
print(P_nAB)
```
These results show that in case the alarm is triggered, there is a possibility of about 20% that the product is flawless and a probability of 80% that the product is faulty.