---
title: "Directed Acyclic Graphs"
---

##Assignment
```{r}
library(tidyverse)
library(dagitty)
library(ggdag)
dag <- dagify(
  X ~ Z,
  Y ~ Z,
  Y ~ X,
  coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 1, X = 0)),
  labels = list(X = "Parking spots",
                Y = "Sales",
                Z = "Customers")
)

# Plot DAG
ggdag(dag) +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))
```

```{r}
# Load necessary libraries
library(ggplot2)
library(dagitty)

# Load the data
data <- readRDS("C:\\Users\\Deniz\\Documents\\GitHub\\Causal_Data_Science_Data\\customer_sat.rds")

# Explore the data
head(data)
summary(data)

# Regression without accounting for subscription
model1 <- lm(satisfaction ~ follow_ups, data = data)
summary(model1)

# Regression accounting for subscription
model2 <- lm(satisfaction ~ follow_ups + subscription, data = data)
summary(model2)
```
Model 1:

Intercept = 78.9

Follow-up coefficient = -3.3

Model 2:

Intercept = 26.8

Follow-up coefficient = 2.2
Subscription Premium coefficient = 44.7
Subscription Premium+ coefficient = 18.1


In the model without accounting for subscription (model1), the negative coefficient for follow-up calls suggests that more follow-up calls are associated with lower satisfaction. However, this might be confounded by the type of subscription.

In the model accounting for subscription (model2), the positive coefficient for follow-up calls suggests that, after accounting for subscription type, more follow-up calls are associated with higher satisfaction.

The positive coefficients for the "Premium" and "Premium+" subscription levels suggest that clients with these subscriptions tend to report higher satisfaction compared to the reference level.


```{r}
# Plot the data
ggplot(data, aes(x = follow_ups, y = satisfaction, color = subscription)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Relationship Between Follow-up Calls and Satisfaction",
       x = "Number of Follow-up Calls",
       y = "Satisfaction") +
  theme_minimal()
```
